Package Interconnection

### 2021-09-12 paper/package_interconnection.Rmd
Modify faceted network.

```{r, fig.width=12, fig.height = 6}

pkg_nodes_facet <- pkg_nodes %>%
  filter(first_author %in% c("Ulrike Groemping", "John Lawson", "Robert B. Gramacy"))

@@

ggraph(routes_tidy_facet, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = first_author), size = 4) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3.5) +
  theme_graph() +
  facet_nodes(~first_author) +
  scale_color_manual(values = c("tomato", "#48C9B0", "#F1C40F"), guide = "none") +
  th_foreground(foreground = "grey80",  border = TRUE) 
```

>>>>

```{r, fig.width=12, fig.height = 7}

pkg_nodes_facet <- pkg_nodes %>%
  filter(first_author %in% c("Ulrike Groemping", "John Lawson", "Robert B. Gramacy", 
                             "Kevin Wright", "Shwetank Lall", "Ernesto Barrios"))

@@

ggraph(routes_tidy_facet, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = first_author), size = 4) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3.5) +
  theme_graph() +
  facet_nodes(~first_author) +
  scale_color_manual(values = c("blue", "tomato", "magenta", "#48C9B0", "#C0392B", "#F1C40F"), 
                     guide = "none") +
  th_foreground(foreground = "grey80",  border = TRUE) 
```
